Supplementary Information

### 2015-06-16 manuscript/supplement.tex
described where I got the webs, working on table

  [[list in supplemental (347 GlobalWeb webs \citep{GlobalWeb}), supplemented 
  with 31 food webs used to study the relationship between consumer and resource body sizes (SizeWebs \citep{Brose2006})
  and seven food webs used to study the impact of parasites on network structure (ParWebs \citep{Dunne2013}).
  Of the GlobalWeb webs, 122 were rejected because their original source could not be found or was unpublished (53), they were source or sink
  webs rather than descriptions of an entire community (13), were focused on plant-pollinator, host-parasitoid, or 
  competitive interactions (8, 34, and 2, respectively), described inferred interactions in an extinct community (2), were ``generalized 
  schemes'' rather than being based on empirical observation (8), or because it was not clear which of a variety of 
  described sites the published food web represented (2). (See Table S1 for a list of rejected webs and reasons for their
  exclusion.) For three GlobalWeb webs which included parasites as a minor component of the community, as well as the 
  seven ParWebs webs, we included a modified version of each web which included only free-living species and the 
  interactions between them \citep{Dunne2013}. 
  As we were considering the log of proportions of basal resources, top predators, and intermediate consumers, each web used in our analysis 
  had to have at least one species in each trophic group.

  of  the University of Canberra's GlobalWeb database (www.globalwebdb.com) 
  \citep{}. Of these, 302 webs had accessible original sources. 
  18 source and sink webs, which describe links to or from a focal taxon, were excluded as they are likely 
  to have different food web properties than webs attempting to
  describe the entire community of a site \citep{Williams2002}, as were 8 plant-pollinator, 34 host-parasitoid, and 2 
  competition-focused networks
  \citep{Riede2010}. Of the remaining 230 food webs, we excluded two paleowebs (comprised of probable interactions 
  between extinct or prehistoric species) \citep{Simenstad1978} and five ``generalized schemes'' 
  \citep{Nybakken1982,Percival1929,Swan1961,Landry1977,Petipa1979,Harrison1963}, as 
  we wished to measure
  directly observed rather than inferred interactions. We further excluded a food web aggregated from several sites in 
  the Pacific Ocean which were widely spread in both latitude and longitude and at markedly different successional stages
  \citep{Vinogradov1978}, such that it is not clear which site the food web represents. 
  This left 223 food webs with widely varying levels of taxonomic resolution, 11 of which contained humans.

>>>>

  We combined published food webs from~\citet{GlobaWeb} (GlobalWeb),~\citet{Brose2006} (Brose), 
  and~\citet{Dunne2013} (Dunne).
  Of the 385 food webs available from~\citet{Globalweb}, 122 were rejected because their original
  source was unpublished or could not be retrieved. We further eliminated 13 source or sink webs
  (which describe feeding links flowing from or to a particular resource or top predator rather
  than the interactions of an entire community), 8 plant-pollinator webs, 34 host-parasitoid webs,
  and 2 networks describing competitive interactions. Finally, we eliminated 2 webs describing 
  inferred interactions in an extinct community, 8 ``generalized schemes'' that were not based
  on direct field data, and 2 webs where it was not clear which of several described study sites
  were used to construct the food web (and therefore the latitude of the food web could not be 
  included). This left us with 156 webs from~\citet{GlobalWeb}.

  To these, we added 7 webs from~\citet{Dunne2013} that were originally used to assess the roles
  of parasites within food webs. As all but 3 of the webs from~\citet{GlobalWeb} contained only
  free-living species, we removed the the parasites (and all interactions involving them) from
  these webs (and the 3 webs containing parasites from~\citet{GlobalWeb}) leaving free-living 
  species only. In addition, we included the 96 webs from~\citet{Brose2006}, which were originally
  collected to XXXYYYY. This gave us a database of 259 webs. However, as we wished to use the
  logarithmic form of power-law relationships, we then eliminated any food web which did not have
  at least one each of basal resources, intermediate consumers, and top predators (to obtain non-zero
  proportions of each category). Our final sample size was thereby reduced to 163 food webs.

 (See Table S1 for a list of rejected webs and reasons for their
  exclusion.)
